Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
answering a comment
Removed parentheses from section 4.3

However, as in the case of new books only some descriptive data are available 
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

@@

Model tree models can learn and tackle tasks with high dimensionality (up to 
hundreds of attributes) and generate reproducible and comprehensible representations, 
what makes them potentially more successful in the eyes of decision makers.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function (Euclidean, Minkowsky or minimax).

@@

 \item \emph{Random Forest}: This method is based in the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
The result is the average of the generated trees during the process.

@@

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximising the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

>>>>

However, as in the case of new books only some descriptive data are available,
compared to those cases in which historical data on sales of published books 
is available, not all forecasting methods can be used in this specific problem.

@@

Model tree models can learn and tackle tasks with high dimensionality, even up to 
hundreds of attributes, and generate reproducible and comprehensible representations, 
what makes them potentially more successful in the eyes of decision makers.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.

@@

 \item \emph{Random Forest}: This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
The result is the average of the generated trees during the process.

@@

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximising the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.
